### 2020-01-15 README.Rmd
Add class RepeatedSpCVCoords + vignette (#30)
* add class `RepeatedSpCVCoords`

* skip vdiffr tests on CI

* add a "Getting Started" vignette

| Literature             | Package                                                   | Reference     | Class Name                      | mlr3 Sugar                     |
| ---------------        | ---------                                                 | ---------     | --------------------            | ---------------------          |
| Spatial Buffering      | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResamplingSpCVBuffer`          | `rsmp("spcv-buffer")`          |
| Spatial Blocking       | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResamplingSpCVBlock`           | `rsmp("spcv-block")`           |
| Spatial CV             | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `ResamplingSpCVCoords`          | `rsmp("spcv-coords")`          |
| Environmental Blocking | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResamplingSpCVEnv`             | `rsmp("spcv-env")`             |
| ---                    | ---                                                       | ---           | ---                             | ---                            |
| Repeated Spatial CV    | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `RepeatedRResamplingSpCVCoords` | `rsmp("repeated-spcv-coords")` |

@@

For detailed information on how to use spatial resampling in {mlr3} please read the section about [spatial analysis in the mlr3 book](https://mlr3book.mlr-org.com/spatial.html).

>>>>

| Literature             | Package                                                   | Reference     | Class Name                      | mlr3 Sugar                     |
| ---------------        | ---------                                                 | ---------     | --------------------            | ---------------------          |
| Spatial Buffering      | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResamplingSpCVBuffer`          | `rsmp("spcv-buffer")`          |
| Spatial Blocking       | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResamplingSpCVBlock`           | `rsmp("spcv-block")`           |
| Spatial CV             | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `ResamplingSpCVCoords`          | `rsmp("spcv-coords")`          |
| Environmental Blocking | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResamplingSpCVEnv`             | `rsmp("spcv-env")`             |
| ---                    | ---                                                       | ---           | ---                             | ---                            |
| Repeated Spatial CV    | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `RepeatedResamplingSpCVCoords` | `rsmp("repeated-spcv-coords")` |

@@

For detailed information on how to use spatial resampling in {mlr3} please read the section about [spatial analysis in the mlr3 book](https://mlr3book.mlr-org.com/spatial.html) and consult the [Getting Started](https://mlr3spatiotempcv.mlr-org.com/articles/mlr3spatiotempcv.html) vignette.
